Homework

### 2016-06-30 Macro Impacts.tex
Added some incorrect work.
Some new stuff. Almost there...
Got it. Neat stuff happens

>>>>

In Fourier space we have
-\Sigma_{xx}&=2k_x(k_y A_z-k_z A_y)\,,\\
-\Sigma_{yy}&=2k_y(k_z A_x-k_x A_z)\,,\\
-\Sigma_{zz}&=2k_z(k_x A_y-k_y A_x)\,,\\
-\Sigma_{xy}&=(k_y^2-k_x^2) A_z+k_z(k_x A_x-k_y A_y)\,,\\
-\Sigma_{yz}&=(k_z^2-k_y^2) A_x+k_x(k_y A_y-k_z A_z)\,,\\
-\Sigma_{zx}&=(k_x^2-k_z^2) A_y+k_y(k_z A_z-k_x A_x)\,.
First observe that any three of these equations together forms a singular linear system.
Taking the sum of 31-33 yields
0&=\Sigma_{xx}+\Sigma_{yy}+\Sigma_{zz}\,.
Observe that
\f{-\Sigma_{xx}k_y}{2k_xk_z}&=\f{k_y^2}{k_z}A_z-k_yA_y\,,\\
\f{-\Sigma_{yy}k_x}{2k_yk_z}&=k_xA_x-\f{k_x^2}{k_z}A_z\,,\\
\f{-\Sigma_{xy}}{k_z}&=\ps{\f{k_y^2-k_z^2}{k_z}}A_z+k_xA_x-k_yA_y\,.
Taking the sum of the first two reveals that
2k_xk_y\Sigma_{xy}&=k_y^2\Sigma_{xx}+k_x^2\Sigma_{yy}\,.
If you want to be silly, we find
0&=(\Sigma_xk_y-\Sigma_yk_x)^2\,.
Anyway, we then have the system of three equations
2k_xk_y\Sigma_{xy}&=k_y^2\Sigma_{xx}+k_x^2\Sigma_{yy}\,,\\
2k_yk_z\Sigma_{yz}&=k_z^2\Sigma_{yy}+k_y^2\Sigma_{zz}\,,\\
2k_zk_x\Sigma_{zx}&=k_x^2\Sigma_{zz}+k_z^2\Sigma_{xx}\,.
which are non-singular. They yield
\Sigma_{xx}&=\f{k_x}{k_yk_z}\p{k_z\Sigma_{xy}-k_x\Sigma_{yz}+k_y\Sigma_{zx}}\,,\\
\Sigma_{yy}&=\f{k_y}{k_zk_x}\p{k_z\Sigma_{xy}+k_x\Sigma_{yz}-k_y\Sigma_{zx}}\,,\\
\Sigma_{zz}&=\f{k_z}{k_xk_y}\p{-k_z\Sigma_{xy}+k_x\Sigma_{yz}+k_y\Sigma_{zx}}\,.
This reveals two facts. The first fact is that the only relevant equations are 34-36. The second is that 37 implies that
0&=k^2\ps{\f{\Sigma_{yz}}{k_yk_z}+\f{\Sigma_{zx}}{k_zk_x}+\f{\Sigma_{xy}}{k_xk_y}}\,.
